|

### 2023-07-20 paper/01-introduction.Rmd
revise statement about multilevel model in intro

In this paper, we focus on the evaluation of defensive linemen in football.
We propose STRAIN, a metric for measuring pass rush effectiveness, inspired by the concept of strain rate in materials science.
Our statistic gives a continuous measure of pressure for every pass rusher on the football field over the course of an entire play.
This allows for the assessment of pass rush success even on plays that do not result in an observed outcome like a sack, hit, or hurry.
We view this as a major step forward for accurately evaluating defensive linemen performance.
We also demonstrate that STRAIN is a stable quantity over time and predictive of defensive pressure.
Additionally, we consider a multilevel model to estimate every pass rusher's contribution to the average STRAIN in a play while controlling for other positions like QB and pass blocker as well as various play-level information.
We note that although our focus in this paper is on pass rushers, our approach can be extended to the evaluation of pass blockers in American football.

>>>>

In this paper, we focus on the evaluation of defensive linemen in football.
We propose STRAIN, a metric for measuring pass rush effectiveness, inspired by the concept of strain rate in materials science.
Our statistic gives a continuous measure of pressure for every pass rusher on the football field over the course of an entire play.
This allows for the assessment of pass rush success even on plays that do not result in an observed outcome like a sack, hit, or hurry.
We view this as a major step forward for accurately evaluating defensive linemen performance.
We also demonstrate that STRAIN is a stable quantity over time and predictive of defensive pressure.
Additionally, we consider a multilevel model to estimate every pass rusher's contribution to the average STRAIN in a play while controlling for team and various play-level information.
We note that although our focus in this paper is on pass rushers, our approach can be extended to the evaluation of pass blockers in American football.
